Assessing Usability of Tor Browser

### 2015-04-10 PETS2015-paper/paper.tex
Minor fixes.

\section{What we already did/background stuff}
Tor is the most widely used anonymity browser today. However, there are complaints that Tor is not usable. Norcie did an experiment \cite{norcie2012eliminating} which identified stopping points in Tor browser, finding out when people would get frustrated with Tor so much they would stop using it. But what about the people who are using Tor? what usability issues would thee be if people were not stopped?

@@

\noindent {\bfseries Experiment Execution Details} 
{\color {red} this subsection might be too much}We plan to recruit at least 120 (to 200?) users for the purpose of this study. This study will be performed at the Experimental Social Science Laboratory (Xlab) at the University of California, Berkeley. The laboratory space consists of 36 Toshiba Tecra R850 laptops in 6 rows of 6 laptops each, with cubicle walls separating each laptop. We used individual host firewalls to simulate the censorship environments. We plan to write a browser extension to measure when users visit what websites in order to log which websites they were successfully able to visit. The total length of the experiment should be less than an hour. Participants will be compensated \$30 for their time, which is more to cover minimum wage and transportation costs.  \\

@@

\noindent {\bfseries List of Tasks} 
We will divide our participants into treatments
by censorship environment.
All participants will be asked to complete the same
list of tasks.
We constructed the list by looking at some of the top
Alexa sites and imagining what might be reasonable
and relevant tasks for each
(that do not require a participant to reveal private information
like passwords).
The tasks are not all intended to be challenging to complete.
Some may not even require the use of Tor Browser,
depending on the censorship environment in effect.

>>>>

\section{What we already did/background stuff}
Tor is the most widely used anonymity browser today. However, there are complaints that Tor is not usable. Norcie~\cite{norcie2012eliminating} did an experiment which identified stopping points in Tor browser, finding out when people would get frustrated with Tor so much they would stop using it. But what about the people who are using Tor? what usability issues would thee be if people were not stopped?

@@

\noindent {\bfseries Experiment Execution Details} 
{\color {red} this subsection might be too much}We plan to recruit at least 120 (to 200?) users for the purpose of this study. This study will be performed at the Experimental Social Science Laboratory (Xlab) at the University of California, Berkeley. The laboratory space consists of 36 laptops with cubicle walls separating each laptop. We used individual host firewalls to simulate the censorship environments. We plan to write a browser extension to measure when users visit what websites in order to log which websites they were successfully able to visit. The total length of the experiment should be less than an hour. Participants will be compensated \$30 for their time, which is more to cover minimum wage and transportation costs.  \\

@@

\noindent {\bfseries List of Tasks} 
We will divide our participants into treatments
by censorship environment.
All participants will be asked to complete the same
list of tasks.
We constructed the list by looking at some of the top
Alexa sites and imagining what might be reasonable
and relevant tasks for each
(that do not require a participant to reveal private information
like passwords).
The tasks are not all intended to be challenging to complete.
